The Diminishing Returns of Music in the Digital Era

### 2024-04-14 paper/paper.qmd
updates to data section

library(tidyverse)
library(palmerpenguins)
```

@@

The inflation adjustment applied to the revenue figures is particularly noteworthy, as it allows for an equitable comparison of the industry's financial status year-over-year, accounting for the changing value of money.

@@

>>>>

library(tidyverse)
library(knitr)
library(readr)
library(ggplot2)
library(palmerpenguins)
```

@@

The inflation adjustment applied to the revenue figures is particularly noteworthy, as it allows for an equitable comparison of the industry's financial status year-over-year, accounting for the changing value of money. Bias should be taken into consideration as the method of revenue tracking has evolved with technology and industry standards.

@@

## Data Characteristics {#sec-characteristics}

The RIAA dataset published by @RIAA did not require any further data cleaning. @tbl-averagerevenue shows how in this sample, the most valuable format of music consumption is the CD. This is because CDs are cheap to produce and there is a larger return on investment because they are physical format which have a larger cost than digital formats to the consumer. The least valuable format of music consumption is the music video. This may be in part due to the fact that music videos are immensely costly and they are slowly losing traction due to the rise in social media.
```{r}
#| echo: false
#| eval: true
#| label: tbl-averagerevenue
#| tbl-cap: "Music Industry Average Revenue per Format"
#| warning: false
#| results: asis
#| 
music_data <- read_csv("/Users/victortimir/music-industry-analysis/data/raw_data/musicdata-1.csv")

average_revenue_per_format <- music_data %>%
  mutate(value_actual = as.numeric(value_actual)) %>%
  filter(value_actual > 0) %>%
  group_by(format) %>%
  summarise(average_revenue = mean(value_actual, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(average_revenue))

average_revenue_per_format$average_revenue <- round(average_revenue_per_format$average_revenue, 2)

average_revenue_table <- kable(head(average_revenue_per_format, 20), 
                               padding = 5, 
                               format = "markdown",
                               digits = 2
                               )

print(average_revenue_table)
```
